---
title: "Alcohol vs Seat choice"
author: "Leia"
date: "summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

## introduction 

$H_O$ there is no difference in the alcohol consumed based on the row you sit in

$H_O$ there is no difference in the alcohol consumed based on the row you sit in 

# method 

the response variable is numerical and the explanatory variable is categorical. Therefore for we use numerical~cat.  

## results  


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
The alcohol consumed in the back is higher then the ones who sit in the front/ middle. 

  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```


this box plot shows that the back seat people drink more than the people who sit in the front and middle. 


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

this data shows the mean and median of alcohol consumed.it also show how many people drink by each quarter. The people in the back drink way more than the people in the front and middle. 


## Inferential Tests

## Conclusions


