---
title: "Alcohol vs Seat choice"
author: "Leia"
date: "summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

## introduction 

$H_O$ there is no difference in the alcohol consumed based on the row you sit in

$H_O$ there is no difference in the alcohol consumed based on the row you sit in 

# method 

the response variable is numerical and the explanatory variable is categorical. Therefore for we use numerical~cat.  

## results  


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
The alcohol consumed in the back is higher then the ones who sit in the front/ middle. 

  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```


this box plot shows that the back seat people drink more than the people who sit in the front and middle. 


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

this data shows the mean and median of alcohol consumed.it also show how many people drink by each quarter. The people in the back drink way more than the people in the front and middle. 


## Inferential Tests

```{r}
model.1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model.1)
```

the p value is 0.0001116 which is less than 0.05. the p value is smaller so therefore we reject the null hypothesis. tis mean that there is a difference in alcohol consumption based on where they sit.  


```{r}
plot(TukeyHSD(model.1))
```

we dont have evidence that there is a difference in the alcohol consumption between the middle and front rows. the only difference we found is the back row consumes more than the middle front row.

## Conclusions

is there a difference between the alcohol consumed between the row you choose to sit in? yes there is no difference between the alcohol consumed by the row you sit in. Based on the data the back row consumed more alcohol than the people who sit in the front and middle row. the p is 0.0001116 which is smaller than 0.05 I will reject the null hypothesis. therefore the back row people consume more alcohol. 
